Exploring the Relationship between Family Background and Children's Education Level in the United States (2021)

### 2023-04-18 outputs/paper/paper.qmd
small changes

# Data {#sec-data}

@@

The number of observations before data cleaning is 4032. This number decrease to 3794 because some rows with missing values. are dropped from the data.

@@

```{r}
#| label: fig-educ
#| fig-cap: Histogram of Respondents' Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

@@

tb_reg_avg <- cleaned_data %>%
  group_by(reg16) %>%
  summarise(mean_educ = round(mean(educ), digits = 2))
tb_reg <- tb_reg %>% mutate("Mean of Education" = tb_reg_avg$mean_educ)
colnames(tb_reg) <- c("Region", "Count", "Percent", "Mean of Education")
tb_reg %>% kable()
```

@@

```{r}
#| label: fig-region
#| fig-cap: Respondent's Living Region at Age of 16 v.s. Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

@@

According to the US News rankings in 2022, these are the top 8 high schools in the US. Thomas Jefferson High School for Science and Technology is located in the South Atlantic region in Virginia, as is the Academic Magnet High School in South Carolina and the School for Advanced Studies (SAS) in Florida. The Signature School can be found in the East North Central region in Indiana, while the Payton College Preparatory High School is also located in the East North Central region in Illinois. The Davidson Academy of Nevada is situated in the Mountain region in Nevada. The Central Magnet School is in the East South Central region in Tennessee, and The School for the Talented and Gifted (TAG) is located in the West South Central region in Texas. [@best]

@@

In the @tbl-lmeduc, a logistic model is employed with the degree as the response variable. However, using a linear regression model with years of education as the response variable may provide a more detailed examination of the factors involved. A linear regression can help analyze specific relationships, such as how years of education change with a five-unit increase in parents' prestige scores. This study opted not to use the linear model due to violations of underlying assumptions. Future research may improve upon this by constructing a more sophisticated linear regression model to elucidate the relationship between these variables in a more precise manner.

>>>>

417 add a paragraph for each section

# Data {#sec-data} (417 add the graph for data)

@@

The number of observations before data cleaning is 4032. This number decreases to 3794 because some rows with missing values. are dropped from the data.

@@

```{r}
#| label: fig-educ
#| fig-cap: Distribution of Respondents' Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

@@

tb_reg_avg <- cleaned_data %>%
  group_by(reg16) %>%
  summarise(mean_educ = round(mean(educ), digits = 2))
tb_reg <- tb_reg %>% mutate("Mean of Education" = tb_reg_avg$mean_educ)
colnames(tb_reg) <- c("Region", "Count", "Proportion", "Mean of Education")
tb_reg %>% kable()
```

@@

```{r}
#| label: fig-region
#| fig-cap: Respondent's Living Region at Age of 16 with Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

@@

According to the US News rankings in 2022, these are the top 8 high schools in the US. Thomas Jefferson High School for Science and Technology is located in the South Atlantic region in Virginia, as is the Academic Magnet High School in South Carolina and the School for Advanced Studies (SAS) in Florida. The Signature School can be found in the East North Central region in Indiana, while the Payton College Preparatory High School is also located in the East North Central region in Illinois. The Davidson Academy of Nevada is situated in the Mountain region in Nevada. The Central Magnet School is in the East South Central region in Tennessee, and The School for the Talented and Gifted (TAG) is located in the West South Central region in Texas [@best].

@@

In the @tbl-lmeduc, a logistic model is employed with the degree as the response variable. However, using a linear regression model with years of education as the response variable may provide a more detailed examination of the factors involved. A linear regression can help analyze specific relationships, such as how years of education change with a five-unit increase in parents' prestige scores. This study opted not to use the linear model due to violations of underlying assumptions. Future research may improve upon this by constructing a more sophisticated linear regression model to demonstrate the relationship between these variables in a more precise manner.
